Explain urban regional function

### 2018-11-10 paper.tex

%explain implementation, we need to incorporate activity and online sentiment
In this paper,to make the results more convincing, we build a system that provides explanations for our functional region clustering results.
We build our system upon two data sets. One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
We combined the urban computing using mobility data with sentiment analysis using geo-content.
As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

\begin{figure}
\centering
\subfigure[An example of our identification result]{
\label{real-map} %% label for first subfigure
\includegraphics[width=2.25in]{example-net.png}}
\subfigure[moving patterns]{
\label{patterns} %% label for second subfigure
\includegraphics[width=2in]{example-line.png}}
\subfigure[Sentiment labels with their probability]{
\label{POI} %% label for second subfigure
\includegraphics[width=2in]{example-POIs.png}}
\subfigure[POIs in different functional region]{
\label{sentiment} %% label for second subfigure
\includegraphics[width=2in]{example-sentiment.png}}
\caption{The explanation provided for functional region identification.
Region I in Fig.\ref{real-map} is labeled as residential region while II is commercial region.
Fig.\ref{patterns} revealed differences of the mobility patterns between residential region and commercial region,workdays and weekends.
Fig.\ref{POI} shows the distribution of POIs within the two regions,e.g. there is more shops in commercial region.
And from fig.\ref{sentiment} we find that people have a more interest in a positive sentiment in traffic for commercial and pay more attention to noise for residential region.}
\label{explanation-example} %% label for entire figure
\end{figure}

@@

\section{System Overview}
We proposed a novel framework to make an explanation for the functional region identification.

@@

\subsection{Preliminary: Latent Factor Model and Matrix factorization}

@@

\subsection{Preliminary: Kernel Function}
%what is kernel function

@@

\section{Experiments}
\subsection{Data Set}
The data set for our experiments including both mobility data and content data.
The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.

@@

The main road data is present in Fig.\ref{raw_map}, including motorway, trunk, primary, secondary, tertiary and their links.
But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
\begin{figure}
\centering
\subfigure[Original segment of city]{
\label{raw_map} %% label for first subfigure
\includegraphics[width=1.5in]{chengdu_1.png}}
\subfigure[After dilation operator]{
\label{dilation} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_2.png}}
\subfigure[After thinning operator]{
\label{thinning} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_3.png}}
\caption{The preparation process of road network}
\label{dilation and thinning} %% label for entire figure
\end{figure}

>>>>

%explain implementation, we need to incorporate activity and online sentiment
\textbf{Our Framework.}
In this paper,to make the results more convincing, we build a system that provides explanations for functional region clustering results.
The system is built upon two data sets. One is mobility data including 3 million pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
We combined the urban computing using mobility data with sentiment analysis using geo-content.
As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

\begin{figure}
\centering
\subfigure[An example of our identification result]{
\label{real-map} %% label for first subfigure
\includegraphics[width=1.5in]{example-net.png}}
\subfigure[moving patterns]{
\label{patterns} %% label for second subfigure
\includegraphics[width=1.4in]{example-line.png}}
\subfigure[POIs in different functional region]{
\label{sentiment} %% label for second subfigure
\includegraphics[width=1.4in]{example-sentiment.png}}
\caption{The explanation provided for functional region identification.
Region I in Fig.\ref{real-map} is labeled as residential region while II is commercial region.
Fig.\ref{patterns} revealed differences of the mobility patterns between residential region and commercial region,workdays and weekends.
Fig.\ref{POI} shows the distribution of POIs within the two regions,e.g. there is more shops in commercial region.
And from fig.\ref{sentiment} we find that people have a more interest in a positive sentiment in traffic for commercial and pay more attention to noise for residential region.}
\label{explanation-example} %% label for entire figure
\end{figure}

@@

\section{System Overview}
We proposed a novel framework to make an explanation for the functional region identification.
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.3]{overview.png}
  \caption{The overview structure of our framework}
\end{figure}

@@

\subsection{Latent Factor Model and Matrix factorization}

@@

\subsection{Model:Kernel Function}
%what is kernel function

@@

\section{Experiments}
\subsection{Data Set}
The data set for our experiments including both mobility data and content data.
The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.
\begin{table}[h]
\caption{Statistics of datasets}\label{dataset}
\begin{tabular}{|l|l|l|}
\hline
Datasets &  attributes & Value\\
\hline
comments & shops with coordinates(POI) & \\
 & shops with comments & \\
 & total comments & \\
\hline
taxicabs & effective orders & 7065937\\
 & effective days & 30 \\
\hline
road networks & geographical scope & [103.93$^\circ$E,104.21$^\circ$E] and [30.56$^\circ$N,30.79$^\circ$N]\\
 & \#road segments & 3589\\
 & percentage of major roads & 24.9\%\\
 & segmented regions & \\
\hline
\end{tabular}
\end{table}

@@

The main road data is present in Fig.\ref{raw_map}, including motorway, trunk, primary, secondary, tertiary and their links.
But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
\begin{figure}[h]
\centering
\subfigure[Original segment of city]{
\label{raw_map} %% label for first subfigure
\includegraphics[width=1.5in]{chengdu_1.png}}
\subfigure[After dilation operator]{
\label{dilation} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_2.png}}
\subfigure[After thinning operator]{
\label{thinning} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_3.png}}
\caption{The preparation process of road network}
\label{dilation and thinning} %% label for entire figure
\end{figure}
